Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-06 docs/msr.tex
minor change

\begin{abstract}
%\boldmath
Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.
In this paper, we present how we used the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. In particular, we analyzed every artifact of the repository by using a
popular static analysis tool. Then by taking advantage of the various features of
the repository (multiple versions for every project, dependencies) we studied
the evolution of security bugs through time and their relationship with the
size of the corresponding artifact and other categories. Also, based on the
dependencies of artifacts we constructed the graph of the repository and
studied the most popular nodes in terms of their PageRank. 
\end{abstract}

>>>>

\begin{abstract}
%\boldmath
Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.
In this paper, we present how we used the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. In particular, we analyzed every artifact of the repository by using a
popular static analysis tool. Then by taking advantage of the various features of
the repository (multiple versions for every project, dependencies) we studied
the evolution of security bugs through time and their relationship with the
size of the corresponding artifact and other bug categories. Also, based on the
dependencies of artifacts we constructed the graph of the repository and
studied the most popular nodes in terms of their PageRank. 
\end{abstract}
